Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-09 manuscript/manuscript.Rmd
fixed yaml and cross reference bugs

author_note: >

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
csl               : "apa7.csl"
class             : "man"
output            : 
  papaja::apa6_pdf:
    includes:
        after_body: "supplementary_information.tex"

@@

We classified articles as ‘not fully reproducible’ (any major numerical discrepancies, decision errors, or insufficient information to proceed) or ‘reproducible’ (no numerical discrepancies or minor numerical discrepancies only) and noted whether author involvement was provided or not. We recorded the potential causal loci of non-reproducibility and judged the likelihood that non-reproducibility impacted conclusions drawn in the original articles. Team members provided a subjective estimate of the time they spent on each reproducibility check. Additional design details are available in Supplementary Information \@ref(sup_design).

@@

The sample was based on a corpus of psychology articles that had been examined in a previous project investigating the impact of an “open badges” scheme introduced at Psychological Science [@kidwell2016]. This sample was selected because the open badges scheme and assessment of reusability by @kidwell2016 enabled us to largely circumvent upstream issues related to data availability and data management and instead focus on downstream issues related to analytic reproducibility. A precision analysis indicates that the sample size affords adequate precision for the purposes of gauging policy compliance (Supplementary Information \@ref(sup_sample)).

Of `r data_kidwell_badge %>% nrow()` articles marked with an open data badge, Kidwell and colleagues had identified `r data_kidwell_badge_reusable %>% nrow()` with datasets that met four reusability criteria (accessible, correct, complete, and understandable). For each of these articles, one investigator (TEH) attempted to identify a coherent set of descriptive and inferential statistics (e.g., means, standard deviations, t-values, p-values; see Figure \@ref(fig:valueTypePlot)), roughly 2-3 paragraphs of text, sometimes including a table or figure, related to a ‘substantive’ finding based on ‘relatively straightforward’ analyses. We focused on substantive findings because they are the most important and straightforward analyses to ensure that our team had sufficient expertise to re-run them. In total, `r nrow(data_values)` discrete numerical values reported in `r totalArticles` articles published between January 2014 and May 2015 were designated as target values. Further information about the sample is available in Supplementary Information \@ref(sup_sample).

@@

To minimize error and facilitate reproducibility, each reproducibility check was conducted by at least two team members who documented the reanalysis process in an R Markdown report (available at https://osf.io/hf9jy/). If articles were initially classified as not fully reproducible, we emailed the author(s) of the article and used any additional information they provided to try and resolve the issues before a final classification was determined. Additional procedural details are available in Supplementary Information \@ref(sup_design).

@@

```{r fig.cap="Forest plot showing the proportion of articles with fully reproducible target values in Hardwicke et al. (2018) and the present study before and after contacting original authors for assistance with reproducibility checks. Squares represent individual study proportions (with size proportional to meta-analytic weighting). Diamonds represent summary proportions estimated by random effects (RE) models. Error bars represent 95% confidence intervals (CIs).", fig.width=8, fig.path="figs/"}
source(here('analysis','meta_analysis.R'))
```

@@

timeSummary <- data_articles %>%
  mutate(activeTTC = (pilotTTC + copilotTTC)/60) %>%
  summarise(median = median(activeTTC), IQR = round(IQR(activeTTC)), min = round(min(activeTTC)), max = round(max(activeTTC)), total = round(sum(activeTTC)))
```
Team members provided concurrent estimates of their time spent on each stage of the analysis. Altogether, they estimated that they spent between `r timeSummary %>% pull(min)` and `r timeSummary %>% pull(max)` (median = `r timeSummary %>% pull(median)`, interquartile range = `r timeSummary %>% pull(IQR)`) hours actively working on each reproducibility check (Supplementary Figure \@ref(fig:timePlot); total time = `r timeSummary %>% pull(total)` hours). This estimate excludes time spent waiting on internal (within our team) and external (with original authors) communications. Availability of original analysis scripts appeared to provide some modest benefits in terms of reproducibility outcomes and time expenditure (see Supplementary Information \@ref(sup_results)).

>>>>

author_note: ""

@@

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
csl               : "apa7.csl"

class             : "man"
output            : 
  papaja::apa6_pdf:
    includes:
        after_body: "supplementary_information.tex"

@@

We classified articles as ‘not fully reproducible’ (any major numerical discrepancies, decision errors, or insufficient information to proceed) or ‘reproducible’ (no numerical discrepancies or minor numerical discrepancies only) and noted whether author involvement was provided or not. We recorded the potential causal loci of non-reproducibility and judged the likelihood that non-reproducibility impacted conclusions drawn in the original articles. Team members provided a subjective estimate of the time they spent on each reproducibility check. Additional design details are available in Supplementary Information \@ref(supdesign).

@@

The sample was based on a corpus of psychology articles that had been examined in a previous project investigating the impact of an “open badges” scheme introduced at Psychological Science [@kidwell2016]. This sample was selected because the open badges scheme and assessment of reusability by @kidwell2016 enabled us to largely circumvent upstream issues related to data availability and data management and instead focus on downstream issues related to analytic reproducibility. A precision analysis indicates that the sample size affords adequate precision for the purposes of gauging policy compliance (Supplementary Information \@ref(supsample)).

Of `r data_kidwell_badge %>% nrow()` articles marked with an open data badge, Kidwell and colleagues had identified `r data_kidwell_badge_reusable %>% nrow()` with datasets that met four reusability criteria (accessible, correct, complete, and understandable). For each of these articles, one investigator (TEH) attempted to identify a coherent set of descriptive and inferential statistics (e.g., means, standard deviations, t-values, p-values; see Figure \@ref(fig:valueTypePlot)), roughly 2-3 paragraphs of text, sometimes including a table or figure, related to a ‘substantive’ finding based on ‘relatively straightforward’ analyses. We focused on substantive findings because they are the most important and straightforward analyses to ensure that our team had sufficient expertise to re-run them. In total, `r nrow(data_values)` discrete numerical values reported in `r totalArticles` articles published between January 2014 and May 2015 were designated as target values. Further information about the sample is available in Supplementary Information \@ref(supsample).

@@

To minimize error and facilitate reproducibility, each reproducibility check was conducted by at least two team members who documented the reanalysis process in an R Markdown report (available at https://osf.io/hf9jy/). If articles were initially classified as not fully reproducible, we emailed the author(s) of the article and used any additional information they provided to try and resolve the issues before a final classification was determined. Additional procedural details are available in Supplementary Information \@ref(supdesign).

@@

```{r forestPlot, fig.cap="Forest plot showing the proportion of articles with fully reproducible target values in Hardwicke et al. (2018) and the present study before and after contacting original authors for assistance with reproducibility checks. Squares represent individual study proportions (with size proportional to meta-analytic weighting). Diamonds represent summary proportions estimated by random effects (RE) models. Error bars represent 95% confidence intervals (CIs).", fig.width=8, fig.path="figs/"}
source(here('analysis','meta_analysis.R'))
```

@@

timeSummary <- data_articles %>%
  mutate(activeTTC = (pilotTTC + copilotTTC)/60) %>%
  summarise(median = median(activeTTC), IQR = round(IQR(activeTTC)), min = round(min(activeTTC)), max = round(max(activeTTC)), total = round(sum(activeTTC)))
```
Team members provided concurrent estimates of their time spent on each stage of the analysis. Altogether, they estimated that they spent between `r timeSummary %>% pull(min)` and `r timeSummary %>% pull(max)` (median = `r timeSummary %>% pull(median)`, interquartile range = `r timeSummary %>% pull(IQR)`) hours actively working on each reproducibility check (Supplementary Figure \@ref(fig:timePlot); total time = `r timeSummary %>% pull(total)` hours). This estimate excludes time spent waiting on internal (within our team) and external (with original authors) communications. Availability of original analysis scripts appeared to provide some modest benefits in terms of reproducibility outcomes and time expenditure (see Supplementary Information \@ref(supresults)).
